A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-19 04_Severity_MetaAnalysis.Rmd
add function to backtransform model estimates

# plot the model residuals
plot(rstandard(PMsev_mvPer)$z, ylim=c(-3,3), pch=19)

1 - exp(PMsev_mvPer$b + PMsev_mvPer$b[1])/(1+exp(PMsev_mvPer$b + PMsev_mvPer$b[1]))
logit_estimates <- ifelse(PMsev_mvPer$b == PMsev_mvPer$b[1], PMsev_mvPer$b, PMsev_mvPer$b + PMsev_mvPer$b[1])
1 - inv_logit(logit_estimates)
```

@@

contrast_Ssum <-
   simple_summary(summary(glht(PMsev_mvSQ, linfct = cbind(
      contrMat(rep(1, 6), type = "Tukey")
   )), test = adjusted("none")))

@@

```{r plotsevContrasts}
par(mar = c(5, 13, 4, 2) + 0.1)
plot(glht(PMsev_mvSQ, linfct = cbind(contrMat(rep(
   1, 6
), type = "Tukey"))), yaxt = 'n')
axis(
   2,
   at = seq_along(contrast_Ssum$contrast),
   labels = rev(contrast_Ssum$contrast),
   las = 2,
   cex.axis = 0.8
)
```

>>>>

# plot the model residuals
plot(rstandard(PMsev_mvPer)$z, ylim=c(-3,3), pch=19)
```

```{r logit_estimates}
1 - exp(PMsev_mvPer$b + PMsev_mvPer$b[1])/(1+exp(PMsev_mvPer$b + PMsev_mvPer$b[1]))
logit_estimates <- ifelse(PMsev_mvPer$b == PMsev_mvPer$b[1], PMsev_mvPer$b, PMsev_mvPer$b + PMsev_mvPer$b[1])
1 - inv_logit(logit_estimates)

backtransform <- function(m, input_only = FALSE, intercept) {
   if (input_only == FALSE) {
      intercept <- m$b[1]

      dat <- data.frame(
         estimates = 1 - inv_logit(c(intercept, m$b[-1] + intercept)),
         StdErr = inv_logit(m$se + intercept) - inv_logit(intercept),
         Zval = c(inv_logit(m$z[1]),
                  inv_logit(m$z[-1] + m$z[1]) - inv_logit(m$z[1])),
         Pval = reportP(m$pval, P_prefix = FALSE),
         CI_lb = 1 - c(inv_logit(m$ci.lb[1]), 
                       inv_logit(m$ci.lb[-1] + intercept)),
         CI_ub = 1 - c(inv_logit(m$ci.ub[1]), 
                       inv_logit(m$ci.ub[-1] + intercept)) 
      )
   }
   if (input_only == TRUE) {
      if (missing(intercept))
         stop("'intercept' argument is empty")
     return( inv_logit(m + intercept) - inv_logit(intercept))
   }
   return(dat)
}
backtransform(PMsev_mvPer)
```

@@

contrast_Ssum <-
   simple_summary(summary(glht(PMsev_mvPer, linfct = cbind(
      contrMat(rep(1, 6), type = "Tukey")
   )), test = adjusted("none")))

@@

```{r plotsevContrasts}
par(mar = c(5, 13, 4, 2) + 0.1)
plot(glht(PMsev_mvPer, linfct = cbind(contrMat(rep(
   1, 6
), type = "Tukey"))), yaxt = 'n')
axis(
   2,
   at = seq_along(contrast_Ssum$contrast),
   labels = rev(contrast_Ssum$contrast),
   las = 2,
   cex.axis = 0.8
)
```
